### 2018-09-12 chapter-latex/e1.tex
add all files

\begin{description}
	\item [Test of Hypothesis 1 (Crisp/Vague RT)] Vague instructions actually led to significantly slower responses than crisp instructions, against Hypothesis 1: $\beta=0.058$, $se=0.013$, $t=4.55$, $p<0.001$. When the model was restricted to numeric-only instructions Vague instructions still led to significantly slower responses than crisp instructions $\beta=0.093$, $se=0.021$, $t=4.51$, $p<0.001$. When the model was restricted to verbal-only instructions Vague instructions tended to slow responses, but not significantly: $\beta=0.024$, $se=0.016$, $t=1.46$, $p=0.155$.
	\item [Test of Hypothesis 2 (Numeric/Verbal RT)] There was actually a significant difference between numeric and verbal instructions, with numeric instructions leading to longer responses than verbal instructions, against Hypothesis 2: $\beta0.265=$, $se=0.072$, $t=5.08$, $p<0.001$.
	\item [Test of Hypothesis 3 (Item RT)] Responses took longer as the levels of Item increased, supporting Hypothesis 3: $\beta=0.120$, $se=0.017$, $t=7.11$, $p<0.001$.
\end{description}

>>>>

\begin{description}
	\item [Test of Hypothesis 1 (Crisp/Vague RT)] Vague instructions actually led to significantly slower responses than crisp instructions, against Hypothesis 1 ($\beta=0.058$, $se=0.013$, $t=4.55$, $p<0.001$). When the model was restricted to numeric-only instructions Vague instructions still led to significantly slower responses than crisp instructions ($\beta=0.093$, $se=0.021$, $t=4.51$, $p<0.001$). When the model was restricted to verbal-only instructions Vague instructions tended to slow responses, but not significantly ($\beta=0.024$, $se=0.016$, $t=1.46$, $p=0.155$).
	\item [Test of Hypothesis 2 (Numeric/Verbal RT)] There was actually a significant difference between numeric and verbal instructions, with numeric instructions leading to longer responses than verbal instructions, against Hypothesis 2 ($\beta0.265=$, $se=0.072$, $t=5.08$, $p<0.001$).
	\item [Test of Hypothesis 3 (Item RT)] Responses took longer as the levels of Item increased, supporting Hypothesis 3 ($\beta=0.120$, $se=0.017$, $t=7.11$, $p<0.001$).
\end{description}

### 2018-09-12 chapter-latex/related-work.tex
add all files

A number of answers to Litman’s question have been proposed, but as we have argued elsewhere [REF KvD JPL and REF book], some of the most often cited answers do not hold up to scrutiny. For example,
%
\begin{itemize}
\item It has been proposed that the existence of vague words makes a language more efficient [REF Barwise Cooper]. The idea is that vagueness allows the use of one and the same word (e.g., ``big”) in different situations, which require different standards. For instance, the vague word ``’big” can denote a mouse a well as an elephant. — The idea is plausible, but the problem is that ``big" is efficient not because it is vague (i.e., not because it allows borderline cases) but because it is context dependent. To see this, it suffices to realise that superlatives are not vague, but they {\em are} context dependent: to be ``the biggest $x$" ascribes different sizes to the referent depending on the word $x$. It is for this reason that we can use the word ``biggest” to talk about the biggest mouse, the biggest elephant, and so on. Context-dependence, however, does not imply vagueness.
%
\item It has been proposed that the ability to combine a statement of quantity (along some dimension) with an evaluative statement [REF Veltman]. The idea is that when we say “The patient has a fever”, we do not merely assert that her temperature is above a certain point in the temperature dimension, we also imply that the deviation is large enough to be clinically significant (i.e., something’s not enirely right with the patient). — The problem with this equally plausible idea is that evaluation does not imply vagueness. For example, the medical term “obese” is evaluative (i.e., it’s not healthy to be obese), yet its standard medical definition in terms of Body Mass Index is perfectly crisp.
\end{itemize}
%
The findings on which we are reporting in the present paper will follow a similar pattern: we will explore a possible answer to Litman’s question, only to conclude that it does not stand up to experimental scrutiny.

Charting the utility of vagueness is also the attested aim of a small number of experimental studies. However, to the best of our knowledge, few of these studies have truly focussed on vagueness in the sense on which we are focussing (i.e., they did not address Litman's challenge). Two recent studies can illustrate both issues.

In a series of studies of behaviour modification, \citeauthor{Mishra01042011} manipulated the presentation format of information about quantities in the domains of mental acuity, physical strength, and weight loss. In the weight loss study, participants were told that the study was designed to test the validity of a new (actually fictitious) health index, the HHI (Holistic Health Index). They were told that an ideal HHI score lies in the range of 45 to 55. In a longitudinal study, participants submitted their weight to a computer each week. Participants were told that two algorithms would be used to compute their HHI, and that the two might give different values initially, in which case the true score lay between the two values. In one condition, which the authors called the precise condition, the two algorithms gave the same score. In the other condition, which the authors called the vague condition, one algorithm added 3\% to the score while the other algorithm subtracted 3\% from the score, yielding a range of values whose midpoint was the same as the two values given in the precise condition.

>>>>

A number of answers to Lipman's question have been proposed, but as we have argued elsewhere, it appears that some of these do not to hold up to scrutiny \citep{van2009utility,vanDeemterBook}. For example,
%
\begin{itemize}
\item It has been proposed that the existence of vague words makes a language more efficient \citep{barwiseperry}. The idea is that vagueness allows the use of one and the same word (e.g., ``big'') in different situations, which require different standards. For instance, the vague word ``big'' can denote a mouse a well as an elephant. The idea is plausible, but the problem is that ``big" is efficient not because it is vague (i.e., not because it allows borderline cases) but because it is context dependent. To see this, note for example that superlatives are not vague, but they {\em are} context dependent: ``the biggest $x$" ascribes different sizes to the referent depending on $x$. It is for this reason that we can use the word ``biggest''  to talk about the biggest mouse, the biggest elephant, and so on. Context-dependence, however, does not imply vagueness.
%
\item It has been pointed out that vague words are capable of combining a statement of quantity (along some dimension) with an evaluative statement \citep{veltman}. The idea is that when we say ``The patient has a fever'', we do not merely assert that her temperature lies above a certain value, we also imply that the deviation is large enough to be clinically significant (i.e., something is not right with the patient). The problem with this plausible idea is that evaluation does not imply vagueness. For example, the medical term ``obese'' is evaluative (i.e., it is not healthy to be obese), yet its standard medical definition in terms of Body Mass Index is perfectly crisp, with BMI values above 30 counting as obese.
\end{itemize}
%
Analogous observations can be made about a number of other purported benefits of vagueness; one of the few hypotheses left standing at the moment is the {\em cost reduction} hypothesis, which we mentioned in the previous section. The findings on which we are reporting in the present paper will follow a familiar pattern: we will explore the cost reduction hypothesis, only to conclude that it does not stand up to scrutiny. Our approach, this time, will be experimental: we conduct controlled experiments to investigate the effect that vague expressions have on a hearer.

Charting the utility of vagueness is also the attested aim of a small number of previous experimental studies. But, as it happens, few of these studies have truly focussed on vagueness in the sense on which we are focussing (i.e., they did not address Lipman's challenge). Two recent studies illustrate this issue; let's discuss them briefly.

In a series of studies of behaviour modification, \citet{Mishra01042011} manipulated the presentation format of information about quantities in the domains of mental acuity, physical strength, and weight loss. In the weight loss study, participants were told that the study was designed to test the validity of a new (actually fictitious) health index, the HHI (Holistic Health Index). They were told that an ideal HHI score lies in the range of 45 to 55. In a longitudinal study, participants submitted their weight to a computer each week. Participants were told that two algorithms would be used to compute their HHI, and that the two might give different values initially, in which case the true score lay between the two values. In one condition, which the authors called the precise condition, the two algorithms gave the same score. In the other condition, which the authors called the vague condition, one algorithm added 3\% to the score while the other algorithm subtracted 3\% from the score, yielding a range of values whose midpoint was the same as the two values given in the precise condition.
